Hydras \& Co.

### 2022-05-13 doc/hydra-chapter.tex
revision book (-> p. 28)

\begin{project}
The type \texttt{Hydra} above describes hydras as \emph{plane trees}, i.e., as drawn on a sheet of paper or computer screen. Thus, hydras are \emph{oriented},
and it is appropriate to consider a \emph{leftmost} or \emph{rightmost} head of
the beast. It could be interesting to consider another representation, in which
every non-leaf node has a \emph{multi-set} -- not an ordered list -- of daughters.
\end{project}

@@

For instance, the hydra \texttt{Hy}  of Figure~\vref{fig:Hy} is defined in \emph{Gallina} as follows:

@@

For instance, the hydra \texttt{Hy''} of Fig~\vref{fig:Hy3}  can be defined in \coq{} as follows:

@@

Let us look at the second subgoal of the induction.

@@

We notice that this subgoal does not contain any hypothesis
on the height and size of the hydra \texttt{h}. So, it looks hard to prove the conclusion. Let's stop.

>>>>

\begin{project}
  Our type \texttt{Hydra} describes hydras as
  \emph{plane oriented trees}, i.e., as drawn on a sheet of paper or computer screen. Thus, it is appropriate to consider a \emph{leftmost} or \emph{rightmost} head of
the beast. It could be interesting to consider another representation, in which
every non-leaf node has a \emph{multi-set} -- not an ordered list -- of daughters.
\end{project}

@@

For instance, the hydra \texttt{Hy}  of Figure~\vref{fig:Hy} is defined as follows:

@@

Let us consider for instance the hydra \texttt{Hy''} of Fig~\vref{fig:Hy3}.

@@

Let us look now at the second subgoal of the induction.

@@

We notice that this sub-goal does not contain any hypothesis
on the height and size of the hydra \texttt{h}. So, it looks hard to prove the conclusion. Let's stop.

### 2022-05-13 doc/hydras.tex
minor changes in theories/gaia
reorganization of tex files
revision book (-> p. 28)

\begin{scope}[xshift=-6.5cm]
\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm] (goedel) { Goedel };
\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm,left of=goedel, node distance=1.9cm] (pock) { Pocklington };
\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm,right of=goedel, node distance=1.8cm] (additions) { Additions };
\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm,right of=additions, node distance=1.8cm] (cantor) { Cantor };

@@

\section{How to install the libraries}
\label{sec:orgheadline4}
\begin{itemize}
\item The present distribution has been checked with version 8.14.1 of the Coq proof assistant, with the plug-ins \texttt{coq-paramcoq}, \texttt{coq-equations}
and \texttt{coq-mathcomp-algebra}.

\item Please refer to \href{https://github.com/coq-community/hydra-battles#readme}{the README file of the project}
\end{itemize}

@@

\include{part-hydras}
\include{chapter-primrec}
\part{A few  certified algorithms}

>>>>

\begin{scope}[xshift=-6.5cm]
\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm] (goedel) {Goedel };
\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm,left of=goedel, node distance=1.9cm] (pock) { Pocklington };
\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm,right of=goedel, node distance=1.8cm] (additions) { Additions };
\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm,right of=additions, node distance=1.8cm] (cantor) { Cantor };

@@

\section{How to install the libraries}
\label{sec:orgheadline4}
 The present distribution has been checked with version 8.14.1 of the Coq proof assistant, with a few plug-ins. \emph{Please refer to \href{https://github.com/coq-community/hydra-battle\#readme}{the README file of the project}.}

@@

\include{part-hydras-intro}
\include{hydra-chapter}
\include{ordinal-chapter}
\include{epsilon0-chapter}
\include{ks-chapter}
\include{large-sets-chapter}
\include{gaia-chapter}
\include{schutte-chapter}
\include{Gamma0-chapter}
\include{chapter-primrec}

\part{A few  certified algorithms}
